Paper \#ZW10157

### 2019-01-16 paper/submission/ZW10157-response-1.tex
add suggestions for 2 answers

@@

Third, several of the features of this system are available is
existing systems but are not acknowledged:

>>>>

{\bf Our response:} {\color{red} The AWA is a high charge charge accelerator. The strong non-linearities
justifying the full 3D approach. At the same time AWA is a facility where many different accelerator research experiments take
place. Therefore it is very desirable, and was one of the important research objectives, to come up with a precise, e.g. 3D
model embedded into a multi-objective optimisation framework. The OPAL framework, differentiates itself, being massively paralle,
full 3D and, and simple to use i.e.\ user friendly.}

@@

{\bf Our response:} {\color{red} The statements on the lines  17-19 of our initial submission are misleading, as
the referee correctly recognised. We replace them with the following:

Despite the great success of on-line models, and various model dependent and model independent tuning and 
optimisation techniques, in research facilities such as AWA empirical tuning is still one of the methods used. Due to the 
non-linear problem mainly from space charge, simple and fast models are applicable only in a very 
restricted manner. When it comes to multi-objective optimisation then the situation is even more complicated.
}

Third, several of the features of this system are available in
existing systems but are not acknowledged:
